Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data

### 2014-02-27 paper_dev/article_pp.tex
first section updated

\plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}{change-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{\scriptsize{The specific d=1 models are validated for both RADARSAT2 and AIRSAR datasets.
Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
with p-value being the significant level of the Kolmogorov–Smirnov goodness-of-fit test between the two histograms}}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}  \\
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both RADARSAT2 and AIRSAR datasets}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif

@@

Similarly, Fig. \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
Again, although the histogram is much tighter, the match is visually obvious in all cases.
This qualitative observation is further supported by high significance level (or p-value) of the standard KS goodness-of-fit test.
While a good p-value does not mean automatic acceptance of the model,
  consistently high p-value readings suggest that the proposed model should not be ignored.

@@

Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}}

>>>>

\plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}{change-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{\scriptsize{The specific d=1 models are validated for both RADARSAT2 and AIRSAR datasets.
Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
with p-value being the significant level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms}}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}  \\
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both RADARSAT2 and AIRSAR datasets}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif

@@

Similarly, Fig. \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
Again, although the histogram is much tighter, the match is visually obvious in all cases.
This qualitative observation is further supported by high significance level (or p-value) of the standard Kolmogorov-Smirnov goodness-of-fit test between curves, noted under each graph.
While a good p-value does not ensure automatic acceptance of the model,
  consistently high p-value lend evidence the proposed model has excellent confidence\cite{Kolmogoroff_1941_AMS_461}.

@@

Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
with p-value being the significant level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.}}
